---
title: "Compute Statistics from Card Draws"
output:
  html_document: default
  pdf_document: default
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#install.packages('ggplot2')
#install.packages('dplyr')
library(ggplot2)
library(dplyr)
```

## Card Values

```{r}
card = c('As','2s','3s','4s','5s','6s','7s','8s','9s','10s','Js','Qs','Ks',
         'Ah','2h','3h','4h','5h','6h','7h','8h','9h','10h','Jh','Qh','Kh',
         'Ad','2d','3d','4d','5d','6d','7d','8d','9d','10d','Jd','Qd','Kd',
         'Ac','2c','3c','4c','5c','6c','7c','8c','9c','10c','Jc','Qc','Kc')
value = c(1,2,3,4,5,6,7,8,9,10,10,10,10,
          1,2,3,4,5,6,7,8,9,10,10,10,10,
          1,2,3,4,5,6,7,8,9,10,10,10,10,
          1,2,3,4,5,6,7,8,9,10,10,10,10)
cards = data.frame(card,value)
```


### Histogram of Card Values

```{r, message=FALSE, warning=FALSE, fig.height=4}
ggplot(aes(x=value), data=cards) +
  geom_histogram()
```

### Statistics of the Value Distribution

```{r}
summary(cards$value)
correction <- sqrt((length(cards$value)-1)/length(cards$value))
sd(cards$value)*correction
```

The mean is 6.54, the median is 7.0 and the standard deviation is 3.15.

## Sampled Values 

```{r}
draws = read.csv('draws.csv')

sumFunc <- function(f,s,t) cards[c(card == f),]$value + 
                           cards[c(card == s),]$value + 
                           cards[c(card == t),]$value

sums <-data.frame(sum = apply(draws, 1, function(d) sumFunc(d['first'],d['second'],d['third'])))
```

### Histogram of Sample values

```{r, message=FALSE, warning=FALSE, fig.height=4}
ggplot(aes(x=sum), data=sums) +
  geom_histogram()
```

### Statistics of Sample values

```{r}
summary(sums)
sd(sums$sum)
var(sums$sum)
```

The sample mean is 19.00. The sample median is 18.5. The sample standard deviation is 5.53. The sample variance is 30.55. The interquartile range is 7.

### Estimations based on the sampled distribution

What range of values do you expect 90% of three-card draw sums to fall into?

90% of all draw sums should fall between 10 and 28.

How likely are you to get a draw of at least 20 from a random draw?

Draws of at least 20 should occur with probability approximately 0.4640.

